Can We Crunch the Social Graph on the Cheap?

### 2011-01-26 doc/hotpar2011/softxmt-hotpar2011.tex
modified:   softxmt-hotpar2011.tex

\section{Implementation}
\label{sec:approach}

The goal of our implementation is to use multithreading to tolerate
the latency of random accesses to memory in a global address space
spread across multiple nodes. This goal has three key challenges:
\begin{itemize}
\item {\bf Lightweight multithreading}

  We expect to need hundreds of
  threads to tolerated a cluster's network latency, so our threading
  implementation must have low overhead.

@@

  A thread making a long-latency global memory reference must be able
  to yield and allow other threads to make progress.

@@

  In a system with high degrees of concurrency, lightweight
  synchronization primitives are important.
\end{itemize}
We discuss our approach to solving each of these challenges in
turn. For each one, we discuss both our current single-node
implementation and ideas for a multi-node implementation.

>>>>

\section{Implementation}
\label{sec:approach}
The goal of our implementation is to use multithreading to tolerate
the latency of random accesses to memory in a global address space
spread across multiple nodes. This goal has three key challenges:
\begin{itemize}
\item {\bf Lightweight multithreading}

  We expect to need hundreds of
  threads to tolerate network latency, so our threading
  implementation must have low memory and context switching overheads.

@@

  We will need to keep track of the hundreds of outstanding memory fetch operations required to utilize bandwidth well.

@@

  We must support global synchronization that can proceed without stalling the processing cores.

\end{itemize}
We discuss our approach to solving each of these challenges in
turn. For each one, we discuss both our current single-node
implementation and ideas for a multi-node implementation.
